---
title: Un cours intéressant
subtitle: et didactique !
author: Euclid of Alexandria \texttt{euclid@alexandria.edu}
date: Novembre 2019
fontsize: 10pt
bibliography: library.bib
output:
    beamer_presentation: 
      includes:
        before_body: toc.tex
        after_body: merci.tex
        in_header: headersorbonne.tex
      keep_tex: yes
      highlight: tango
      template: "default.beamer"
---

```{r, echo=FALSE}
default.size <- "scriptsize" ## Taille du code R par defaut (choix possible : "normalsize", "tiny", "scriptsize", 'footnotesize", "small", "large", "Large", "LARGE", "huge", "Huge"). Ne pas modifier ce qu'il y a ci-dessous !
knitr::opts_chunk$set(size = default.size) ## 
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

# In the morning

### Getting up

- Turn off alarm
- Get out of bed

### Breakfast

- Eat eggs
- Drink coffee

### Work

First Euler observed that
$$1 + e^{i \pi} = 0.$$

Then, Gauss discovered the normal distribution:
$$P(x) = \frac{1}{{\sigma \sqrt {2\pi } }}e^{{{ - \left( {x - \mu } \right)^2 } \mathord{\left/ {\vphantom {{ - \left( {x - \mu } \right)^2 } {2\sigma ^2 }}} \right. \kern-\nulldelimiterspace} {2\sigma ^2 }}}$$

Finally, Einstein proclaimed: 
$$E = m C^2$$

At the end, Ioannidis concluded that most published research findings are false [see @Ioannidis_2005]

---


```{r}
summary(cars)
```

---

```{r, size = "normalsize"}
summary(cars)
```

---

```{r}
plot(cars)
```

# In the evening

## Dinner

### Miam!

- Eat spaghetti
- Drink wine

## Going to sleep

### Two simple steps!

- Get in bed
- Count sheep

::: {.alertblock}
### And now...
Good night!
:::

# References

### References
